Tidy data structure to support exploration and modeling of temporal-context data

### 2018-11-11 main.Rmd
rewrote index section

(ref:tb-sub) A small subset of estimates of tuberculosis burden generated by World Health Organisation in 2011 and 2012, with 12 observations and 5 variables. The index refers to column `year`, the key to multiple columns: `contry` nested under `continent` crossed with `gender`, and the measured variable to column `count`.

@@

Time provides a contextual basis for temporal data. The time could range from date-times (such as `POSIXct` and `Date` in R) to year-months, to years.

A variable representing time is indispensable to a tsibble, referred to as "index". The "index" is an intact column instead of an attribute. This accessibility of index promotes transparency and unambiguity while manipulating time. For example, subsetting a certain time period of data, extracting time components (like time of day and day of week), or converting time zones are directly dealt with index. It is also often to join other data tables based on the common time indices. Tools are provided to work with time itself, rather than wrappers to work with a whole data set. This promotes transparency and visibility to make inspection easier. This sets the tone on methods design philosophy: well-structured, expressive and unambiguous workflow.

>>>>

(ref:tb-sub) A small subset of estimates of tuberculosis burden generated by World Health Organisation in 2011 and 2012, with 12 observations and 5 variables. The index refers to column `year`, the key to multiple columns: `country` nested under `continent` crossed with `gender`, and the measured variable to column `count`.

@@

Time provides a contextual basis for temporal data. Time representation could range from date-times (such as `POSIXct` and `Date` in R) to years, to sequential numbers for simulated data for example.

A variable representing time is indispensable to a tsibble, referred to as "index". The "index" is an intact data column rather than an attribute, which makes time accessible to users. For example, one could easily extract time components, such as time of day and day of week, from the index to visualise seasonal effects of response variables. One could also join other data sources to the tsibble based on common time indices. The accessibility of tsibble index motivates data analysis towards transparency and human readability. But if the "index" is employed as attributes, analysts would write these simple queries in a programmatic manner, which can be avoidable from an analytic point of view.
